Note on the hydrogen-bond auto-correlation

### 2014-10-17 writedown/auto.correlations/h.bond.notes/main.tex
rename

\title{Notes on the hydrogen-bond auto-correlation}
\author{Han Wang}
\email{han.wang@fu-berlin.de}
\affiliation{Zuse Institut Berlin, Germany}

\begin{abstract}
  In this note I describe the implementation details of the hydrogen-bond auto-correlations.
\end{abstract}

@@

  \frac{(\vect r_{11}^{\oxy\hyd}\cdot \vect r_{12}^{\oxy\oxy})'r_{11}^{\oxy\hyd}\, r_{12}^{\oxy\oxy} - \vect r_{11}^{\oxy\hyd}\cdot \vect r_{12}^{\oxy\oxy} (r_{11}^{\oxy\hyd}\cdot r_{12}^{\oxy\oxy})'}{ ( r_{11}^{\oxy\hyd}\, r_{12}^{\oxy\oxy} )^2} \\\nonumber

@@

  \\\nonumber  

>>>>

\title{Note on the hydrogen-bond auto-correlation}
\author{Han Wang}
\email{han.wang@fu-berlin.de}
\affiliation{Zuse Institut Berlin, Germany}

\begin{abstract}
  In this note I describe the implementation details of the hydrogen-bond auto-correlation.
\end{abstract}

@@

  \frac{(\vect r_{11}^{\oxy\hyd}\cdot \vect r_{12}^{\oxy\oxy})'r_{11}^{\oxy\hyd}\, r_{12}^{\oxy\oxy} - \vect r_{11}^{\oxy\hyd}\cdot \vect r_{12}^{\oxy\oxy} (r_{11}^{\oxy\hyd}\cdot r_{12}^{\oxy\oxy})'}{ ( r_{11}^{\oxy\hyd}\, r_{12}^{\oxy\oxy} )^2} \\

@@
